Stable Neo-Hookean Flesh Simulation

### 2019-10-31 LaTeX-Master-Vorlage/chapter/Background.tex
working on mahtematical background

@@

>>>>

\begin{definition}[\textbf{Singular Values}]
The singular values of a matrix A $\in$ $\mathbb{R}^{m x n}$ are the square roots of the eigenvalues of $AA^{\mathrm{T}}$.
\end{definition}

The theorem of the singular value decomposition tells us that we can factor every m-by-n matrix into one orthogonal m-by-m, one diagonal m-by-n and one orthogonal n-by-n matrix. More formally:

\begin{theorem}[\textbf{The SVD Theorem}]
Let A $\in$ $\mathbb{R}^{m x n}$ be a matrix having r positive singular values, m $\geq$ n. Then there exist orthogonal matrices U $\in$ $\mathbb{R}^{m x m}$, V $\in$ $\mathbb{R}^{n x n}$ and a diagonal matrix $\tilde{\Sigma}$ $\in$ $\mathbb{R}^{m x n}$ such that

\[
\begin{array}{l}{A=U \tilde{\Sigma} V^{\mathrm{T}}} \\ {\tilde{\Sigma}=\left[\begin{array}{ll}{\Sigma} & {0} \\ {0} & {0}\end{array}\right]}\end{array}
\]

where $\Sigma$ = diag ($\sigma$1, $\sigma$2, . . . , $\sigma$r), and $\sigma$1 $\geq$ $\sigma$2 $\geq$ · · · $\geq$ $\sigma$r $>$ 0 are the positive singular values of A.

\end{theorem}
Reference: \cite{ford2014numerical}, chap. 15

\todoredefined[inline]{
TODO: Check reference. Make paragraphs work together. Add examples.
}

\subsection{Polar Decomposition}

@@

\subsection{Polar Decomposition of the Deformation Gradient}
With the help of mathematics we can decompose the deformation gradient in the following form:

\[
F = R S
\]
